---
title: "Main Survey Analysis"
output: html_document
date: "2025-03-05"
---

```{r, include = F}
## Load packages
library(tidyverse)
library(MOTE)
library(broom)
library(knitr)
library(kableExtra)
library(scales)
library(psych)
library(here)
`%+%` <- paste0


## Load data
data_directory <- "H:\\My Drive\\Research\\Projects\\Depression Symptom Feedback\\Data\\"

# Data for both groups (i.e., full sample)
both_groups <- readRDS(data_directory %+% "Clean Main Survey Data.rds") 

feedback_only <- both_groups %>%
  filter(!group)

intervention_only <- both_groups %>%
  filter(group)


## Create z-scores, by group
both_groups <- both_groups %>%
  mutate(
    across(
      .cols = c(
        matches("^dep_.._t1$"),
        matches("^prob_.._t.$")
      ),
      .fn = ~ as.numeric(scale(.x)),
      .names = "{.col}_z"
    )
  )

feedback_only <- feedback_only %>%
  mutate(
    across(
      .cols = c(
        matches("^dep_.._t1$"),
        matches("^prob_.._t.$")
      ),
      .fn = ~ as.numeric(scale(.x)),
      .names = "{.col}_z"
    )
  )


## Load functions
source(here("Main Survey Analysis Functions.R"))
```

## Descriptive Statistics

### Age

```{r}
both_groups %>%
  summarize(across(age_t1, list(mean = mean, sd = sd, min = min, max = max))) %>%
  print_nicely(2)

both_groups %>%
  group_by(group_char) %>%
  summarize(across(age_t1, list(mean = mean, sd = sd, min = min, max = max))) %>%
  print_nicely(2)
```

### Gender

```{r}
both_groups %>%
  count(gender_t1) %>%
  mutate(pct = percent(n / sum(n), .1)) %>%
  print_nicely(2)

both_groups %>%
  group_by(group_char) %>%
  count(gender_t1) %>%
  mutate(pct = percent(n / sum(n), .1)) %>%
  print_nicely(2)
```

### Sexuality

```{r}
both_groups %>%
  count(sexuality_t1) %>%
  drop_na() %>%
  mutate(pct = percent(n / sum(n), .1)) %>%
  print_nicely(2)

both_groups %>%
  group_by(group_char) %>%
  count(sexuality_t1) %>%
  drop_na() %>%
  mutate(pct = percent(n / sum(n), .1)) %>%
  print_nicely(2)
```

### Race/Ethnicity

```{r}
both_groups %>%
  count(race_eth_t1) %>%
  drop_na() %>%
  mutate(pct = percent(n / sum(n), .1)) %>%
  print_nicely(2)

both_groups %>%
  group_by(group_char) %>%
  count(race_eth_t1) %>%
  drop_na() %>%
  mutate(pct = percent(n / sum(n), .1)) %>%
  print_nicely(2)
```

### PHQ-8 Sum Score

```{r}
both_groups %>%
  summarize(across(phq_8_sum, list(mean = mean, sd = sd, min = min, max = max))) %>%
  print_nicely(2)

both_groups %>%
  group_by(group_char) %>%
  summarize(across(phq_8_sum, list(mean = mean, sd = sd, min = min, max = max))) %>%
  print_nicely(2)
```

### PHQ-8 Categories (Test Result)

```{r}
both_groups %>%
  count(test_result) %>%
  mutate(pct = percent(n / sum(n), .1)) %>%
  print_nicely(2)

both_groups %>%
  group_by(group_char) %>%
  count(test_result) %>%
  mutate(pct = percent(n / sum(n), .1)) %>%
  print_nicely(2)
```

### Self-Labeling (Current)

```{r}
both_groups %>%
  count(self_label_t1) %>%
  mutate(pct = percent(n / sum(n), .1)) %>%
  print_nicely(2)

both_groups %>%
  group_by(group_char) %>%
  count(self_label_t1) %>%
  mutate(pct = percent(n / sum(n), .1)) %>%
  print_nicely(2)
```

### Self-Labeling (Past)

```{r}
both_groups %>%
  count(self_label_ever_t1) %>%
  mutate(pct = percent(n / sum(n), .1)) %>%
  print_nicely(2)

both_groups %>%
  group_by(group_char) %>%
  count(self_label_ever_t1) %>%
  mutate(pct = percent(n / sum(n), .1)) %>%
  print_nicely(2)
```

## Correlations and Alphas

### Depression Beliefs

#### Personal Control

```{r}
both_groups %>%
  select(matches("dep_pc_t1_[0-9]")) %>%
  cor() %>%
  print_nicely(2)

both_groups %>%
  select(matches("dep_pc_t1_[0-9]")) %>%
  alpha() %>%
  pluck("total") %>%
  print_nicely(2)
```

#### Therapy Control

```{r}
both_groups %>%
  select(matches("dep_tc_t1_[0-9]")) %>%
  cor() %>%
  print_nicely(2)

both_groups %>%
  select(matches("dep_tc_t1_[0-9]")) %>%
  alpha() %>%
  pluck("total") %>%
  print_nicely(2)
```

#### Medication control

```{r}
both_groups %>%
  select(matches("dep_mc_t1_[0-9]")) %>%
  cor() %>%
  print_nicely(2)

both_groups %>%
  select(matches("dep_mc_t1_[0-9]")) %>%
  alpha() %>%
  pluck("total") %>%
  print_nicely(2)
```

#### Prognostic pessimism

```{r}
both_groups %>%
  select(matches("dep_pp_t1_[0-9]")) %>%
  cor() %>%
  print_nicely(2)

both_groups %>%
  select(matches("dep_pp_t1_[0-9]")) %>%
  alpha() %>%
  pluck("total") %>%
  print_nicely(2)
```

#### Blame

```{r}
both_groups %>%
  select(matches("dep_bl_t1_[0-9]")) %>%
  cor() %>%
  print_nicely(2)

both_groups %>%
  select(matches("dep_bl_t1_[0-9]")) %>%
  alpha() %>%
  pluck("total") %>%
  print_nicely(2)
```

#### Intercorrelations

```{r}
both_groups %>%
  select(matches("^dep_.._t1$")) %>%
  cor() %>%
  print_nicely(2)

both_groups %>%
  select(matches("^dep_.._t1$")) %>%
  corr.test(adjust = "none") %>%
  pluck("p") %>%
  print_nicely(3)
```

### Problem Beliefs

#### Personal Control

```{r}
both_groups %>%
  select(matches("prob_pc_t1_[0-9]")) %>%
  cor() %>%
  print_nicely(2)

both_groups %>%
  select(matches("prob_pc_t1_[0-9]")) %>%
  alpha() %>%
  pluck("total") %>%
  print_nicely(2)
```

#### Therapy Control

```{r}
both_groups %>%
  select(matches("prob_tc_t1_[0-9]")) %>%
  cor() %>%
  print_nicely(2)

both_groups %>%
  select(matches("prob_tc_t1_[0-9]")) %>%
  alpha() %>%
  pluck("total") %>%
  print_nicely(2)
```

#### Medication Control

```{r}
both_groups %>%
  select(matches("prob_mc_t1_[0-9]")) %>%
  cor() %>%
  print_nicely(2)

both_groups %>%
  select(matches("prob_mc_t1_[0-9]")) %>%
  alpha() %>%
  pluck("total") %>%
  print_nicely(2)
```

#### Prognostic Pessimism

```{r}
both_groups %>%
  select(matches("prob_pp_t1_[0-9]")) %>%
  cor() %>%
  print_nicely(2)

both_groups %>%
  select(matches("prob_pp_t1_[0-9]")) %>%
  alpha() %>%
  pluck("total") %>%
  print_nicely(2)
```

#### Blame

```{r}
both_groups %>%
  select(matches("prob_bl_t1_[0-9]")) %>%
  cor() %>%
  print_nicely(2)

both_groups %>%
  select(matches("prob_bl_t1_[0-9]")) %>%
  alpha() %>%
  pluck("total") %>%
  print_nicely(2)
```

#### Intercorrelations

```{r}
both_groups %>%
  select(matches("^prob_.._t1$")) %>%
  cor() %>%
  print_nicely(2)

both_groups %>%
  select(matches("^prob_.._t1$")) %>%
  corr.test(adjust = "none") %>%
  pluck("p") %>%
  print_nicely(3)
```

#### Comparisons

```{r}
t_test <- function(stem) {
  
  prob <- both_groups[["prob_" %+% stem %+% "_t1"]]
  dep <- both_groups[["dep_" %+% stem %+% "_t1"]]
  
  t <- t.test(prob, dep, paired = T)
  
  d <- d.ind.t(
    m1 = mean(prob),
    sd1 = sd(prob),
    n1 = length(prob),
    m2 = mean(dep),
    sd2 = sd(dep),
    n2 = length(dep)
  )
  
  out <- tibble(
    var = stem,
    prob_mean = mean(prob),
    prob_sd = sd(prob),
    dep_mean = mean(dep),
    dep_sd = sd(dep),
    d_est = d$d,
    d_low = d$dlow,
    d_high = d$dhigh
  )
  
}

map(
  .x = lst("pc", "tc", "mc", "pp", "bl"),
  .f = t_test
) %>%
  bind_rows()
```

#### Visualized

```{r}
both_groups %>%
  select(
    matches("^prob_.._t1$"),
    matches("^dep_.._t1$")
  ) %>%
  pivot_longer(cols = c(matches("^prob_.._t1$"), matches("^dep_.._t1$"))) %>%
  mutate(
    construct = case_when(
      grepl("^prob", name) ~ "Problem Beliefs",
      grepl("^dep", name) ~ "Depression Beliefs"
    ) %>%
      factor(levels = c("Problem Beliefs", "Depression Beliefs")),
    belief = case_when(
      grepl("_pc_", name) ~ "Personal Control",
      grepl("_tc_", name) ~ "Therapy Control",
      grepl("_mc_", name) ~ "Medication Control",
      grepl("_pp_", name) ~ "Prognostic Pessimism",
      grepl("_bl_", name) ~ "(Self-)Blame"
    ) %>%
      factor(levels = c("Personal Control", "Therapy Control", "Medication Control", "Prognostic Pessimism", "(Self-)Blame"))
  ) %>%
  ggplot() +
  geom_histogram(
    aes(value),
    binwidth = 1/3
  ) +
  facet_grid(
    construct ~ belief
  ) +
  theme_classic()
```

## Research Questions

### RQ 1. Average Change in Outcomes

```{r}
bind_rows(
  d_av(feedback_only, "prob_pc"),
  d_av(feedback_only, "prob_tc"),
  d_av(feedback_only, "prob_mc"),
  d_av(feedback_only, "prob_pp"),
  d_av(feedback_only, "prob_bl")
) %>%
  mutate(t_p_adj = p.adjust(t_p, "BH")) %>%
  print_nicely(3)
```

#### RQ 1a. Moderation by Self-Labeling

```{r}
bind_rows(
  regression(feedback_only, prob_pc_t2_z ~ prob_pc_t1_z + self_label_t2_bin),
  regression(feedback_only, prob_tc_t2_z ~ prob_tc_t1_z + self_label_t2_bin),
  regression(feedback_only, prob_mc_t2_z ~ prob_mc_t1_z + self_label_t2_bin),
  regression(feedback_only, prob_pp_t2_z ~ prob_pp_t1_z + self_label_t2_bin),
  regression(feedback_only, prob_bl_t2_z ~ prob_bl_t1_z + self_label_t2_bin)
) %>%
  filter(iv == "self_label_t2_binTRUE") %>%
  mutate(p_adj = p.adjust(p, "BH")) %>%
  print_nicely(3)
```

#### RQ 1b. Moderation by Depression Beliefs

```{r}
bind_rows(
  regression(feedback_only, prob_pc_t2_z ~ prob_pc_t1_z + dep_pc_t1_z),
  regression(feedback_only, prob_tc_t2_z ~ prob_tc_t1_z + dep_tc_t1_z),
  regression(feedback_only, prob_mc_t2_z ~ prob_mc_t1_z + dep_mc_t1_z),
  regression(feedback_only, prob_pp_t2_z ~ prob_pp_t1_z + dep_pp_t1_z),
  regression(feedback_only, prob_bl_t2_z ~ prob_bl_t1_z + dep_bl_t1_z)
) %>%
  filter(grepl("^dep", iv)) %>%
  mutate(p_adj = p.adjust(p, "BH")) %>%
  print_nicely(3)
```

#### Additional Moderation Tests

Self-Labeling * Baseline Belief Interaction

```{r}
bind_rows(
  regression(feedback_only, prob_pc_t2_z ~ prob_pc_t1_z + self_label_t2_bin*dep_pc_t1_z),
  regression(feedback_only, prob_tc_t2_z ~ prob_tc_t1_z + self_label_t2_bin*dep_tc_t1_z),
  regression(feedback_only, prob_mc_t2_z ~ prob_mc_t1_z + self_label_t2_bin*dep_mc_t1_z),
  regression(feedback_only, prob_pp_t2_z ~ prob_pp_t1_z + self_label_t2_bin*dep_pp_t1_z),
  regression(feedback_only, prob_bl_t2_z ~ prob_bl_t1_z + self_label_t2_bin*dep_bl_t1_z)
) %>%
  filter(grepl(":", iv)) %>%
  mutate(p_adj = p.adjust(p, "BH")) %>%
  print_nicely(3)
```

Test Result (_Not_ PHQ-8 Sum)

It's hard to come up with a statistical test that proves the effect is from the test result, rather than from PHQ sum score; they are highly correlated of course (_r_ > .9), so having them in the same model inflates variance. If you try a residual approach, the non-residualized IV (because it owns all the shared variance) is always significant, and the residualized variable is not. The visual argument seems strongest. It's possible that a formal test of regression discontinuity could be used here as well, but that feels too complicated for the time being.

```{r}
bind_rows(
  regression(feedback_only, prob_pc_t2_z ~ prob_pc_t1_z + as.numeric(test_result_fct)),
  regression(feedback_only, prob_tc_t2_z ~ prob_tc_t1_z + as.numeric(test_result_fct)),
  regression(feedback_only, prob_mc_t2_z ~ prob_mc_t1_z + as.numeric(test_result_fct)),
  regression(feedback_only, prob_pp_t2_z ~ prob_pp_t1_z + as.numeric(test_result_fct)),
  regression(feedback_only, prob_bl_t2_z ~ prob_bl_t1_z + as.numeric(test_result_fct))
) %>%
  filter(grepl("test", iv)) %>%
  mutate(p_adj = p.adjust(p, "BH")) %>%
  print_nicely(3)

bind_rows(
  regression(feedback_only, prob_pc_t2_z ~ prob_pc_t1_z + test_result_fct),
  regression(feedback_only, prob_tc_t2_z ~ prob_tc_t1_z + test_result_fct),
  regression(feedback_only, prob_mc_t2_z ~ prob_mc_t1_z + test_result_fct),
  regression(feedback_only, prob_pp_t2_z ~ prob_pp_t1_z + test_result_fct),
  regression(feedback_only, prob_bl_t2_z ~ prob_bl_t1_z + test_result_fct)
) %>%
  filter(grepl("test", iv)) %>%
  mutate(p_adj = p.adjust(p, "BH")) %>%
  print_nicely(3)

# Change at each level
mappable_grid <- expand_grid(
  .x = c("prob_pc", "prob_tc", "prob_mc", "prob_pp", "prob_bl"),
  .y = c("Mild Depression", "Moderate Depression", "Moderately Severe or Severe Depression")
)

map2(
  .x = mappable_grid$.x,
  .y = mappable_grid$.y,
  .f = ~ {
    d_av(
      .data = filter(feedback_only, test_result_fct == .y), 
      var = .x
    ) %>%
      select(d_av_est) %>%
      mutate(var = .x, cat = .y)
  }
) %>% 
  bind_rows() %>%
  pivot_wider(
    id_cols = "var",
    names_from = "cat",
    values_from = "d_av_est"
  )

# Plot for personal control
temp <- lm(data = feedback_only, (prob_pc_t2_z - prob_pc_t1_z) ~ test_result_fct + phq_8_sum)
feedback_only %>%
  mutate(
    actual_change = prob_pc_t2_z - prob_pc_t1_z,
    predicted_change = predict(temp)
  ) %>%
  ggplot(aes(phq_8_sum, actual_change, color = test_result_fct)) +
  geom_line(aes(y = predicted_change), size = 1.5) +
  stat_summary(fun = mean, fun.data = mean_se, geom = "pointrange", alpha = .5) +
  scale_x_continuous(name = "PHQ-8 Sum") +
  scale_y_continuous(name = "Change in Perceived Personal Control (S.D.)") +
  scale_color_discrete(name = "PHQ-8 Test Result") +
  theme_classic()
```

### RQ 2. Intervention Effects

```{r}
bind_rows(
  regression(both_groups, prob_pc_t2_z ~ prob_pc_t1_z + group),
  regression(both_groups, prob_tc_t2_z ~ prob_tc_t1_z + group),
  regression(both_groups, prob_mc_t2_z ~ prob_mc_t1_z + group),
  regression(both_groups, prob_pp_t2_z ~ prob_pp_t1_z + group),
  regression(both_groups, prob_bl_t2_z ~ prob_bl_t1_z + group)
) %>%
  filter(iv == "groupTRUE") %>%
  mutate(p_adj = p.adjust(p, "BH")) %>%
  print_nicely(3)

# d(av)
bind_rows(
  d_av(intervention_only, "prob_pc"),
  d_av(intervention_only, "prob_tc"),
  d_av(intervention_only, "prob_mc"),
  d_av(intervention_only, "prob_pp"),
  d_av(intervention_only, "prob_bl")
) %>%
  print_nicely(3)

# d(ppc2)
bind_rows(
  d_ppc2("prob_pc"),
  d_ppc2("prob_tc"),
  d_ppc2("prob_mc"),
  d_ppc2("prob_pp"),
  d_ppc2("prob_bl")
) %>%
  print_nicely(3)
```

#### RQ 2a. Moderation by Self-Labeling

```{r}
bind_rows(
  regression(both_groups, prob_pc_t2_z ~ prob_pc_t1_z + group*self_label_t2_bin),
  regression(both_groups, prob_tc_t2_z ~ prob_tc_t1_z + group*self_label_t2_bin),
  regression(both_groups, prob_mc_t2_z ~ prob_mc_t1_z + group*self_label_t2_bin),
  regression(both_groups, prob_pp_t2_z ~ prob_pp_t1_z + group*self_label_t2_bin),
  regression(both_groups, prob_bl_t2_z ~ prob_bl_t1_z + group*self_label_t2_bin)
) %>%
  filter(iv == "groupTRUE:self_label_t2_binTRUE") %>%
  mutate(p_adj = p.adjust(p, "BH")) %>%
  print_nicely(3)
```

Visualized:

```{r}
both_groups %>%
  pivot_longer(matches("^prob_.._t.$")) %>%
  mutate(
    construct = name %>%
      str_extract("(?<=_)(.+?)(?=_)") %>%
      factor(
        levels = c("pc", "tc", "mc", "pp", "bl"),
        labels = c(
          "Personal Control",
          "Therapy Control",
          "Medication Control",
          "Prognostic Pessimism",
          "Self-Blame"
        )
      ),
    timepoint = str_extract(name, "..$")
  ) %>%
  group_by(construct, timepoint, group_char, self_label_t2_bin) %>%
  summarize(
    mean = mean(value),
    sd = sd(value),
    n = n(),
    .groups = "drop"
  ) %>%
  mutate(
    se = sd / sqrt(n),
    upper = mean + (1.96 * se),
    lower = mean - (1.96 * se)
  ) %>%
  ggplot(
    aes(
      x = timepoint,
      y = mean,
      color = group_char,
      linetype = self_label_t2_bin,
      group = interaction(group_char, self_label_t2_bin)
    )
  ) +
  geom_line(
    linewidth = 1
  ) +
  geom_errorbar(
    aes(
      ymin = lower,
      ymax = upper
    ),
    size = 1,
    width = .2
  ) +
  scale_x_discrete(name = "Timepoint") +
  scale_y_continuous(name = "Mean (Likert Scale Points)") +
  labs(color = "Received Intervention", linetype = "Self-Label (t2)") +
  facet_grid(group_char ~ construct) +
  theme_classic() +
  theme(panel.grid.major.y = element_line())
```

#### RQ 2b. Moderation by Depression Beliefs

```{r}
bind_rows(
  regression(both_groups, prob_pc_t2_z ~ prob_pc_t1_z + group*dep_pc_t1_z),
  regression(both_groups, prob_tc_t2_z ~ prob_tc_t1_z + group*dep_tc_t1_z),
  regression(both_groups, prob_mc_t2_z ~ prob_mc_t1_z + group*dep_mc_t1_z),
  regression(both_groups, prob_pp_t2_z ~ prob_pp_t1_z + group*dep_pp_t1_z),
  regression(both_groups, prob_bl_t2_z ~ prob_bl_t1_z + group*dep_bl_t1_z)
) %>%
  filter(grepl(":", iv)) %>%
  mutate(p_adj = p.adjust(p, "BH")) %>%
  print_nicely(3)
```

#### Additional Moderation Tests

```{r}
# Test result (controlling for PHQ-8 sum)
bind_rows(
  regression(both_groups, prob_pc_t2_z ~ prob_pc_t1_z + group*test_result_fct + phq_8_sum),
  regression(both_groups, prob_tc_t2_z ~ prob_tc_t1_z + group*test_result_fct + phq_8_sum),
  regression(both_groups, prob_mc_t2_z ~ prob_mc_t1_z + group*test_result_fct + phq_8_sum),
  regression(both_groups, prob_pp_t2_z ~ prob_pp_t1_z + group*test_result_fct + phq_8_sum),
  regression(both_groups, prob_bl_t2_z ~ prob_bl_t1_z + group*test_result_fct + phq_8_sum)
) %>%
  filter(grepl(":", iv)) %>%
  mutate(p_adj = p.adjust(p, "BH")) %>%
  print_nicely(3)

# PHQ-8 sum (controlling for test result)
bind_rows(
  regression(both_groups, prob_pc_t2_z ~ prob_pc_t1_z + group*phq_8_sum + test_result_fct),
  regression(both_groups, prob_tc_t2_z ~ prob_tc_t1_z + group*phq_8_sum + test_result_fct),
  regression(both_groups, prob_mc_t2_z ~ prob_mc_t1_z + group*phq_8_sum + test_result_fct),
  regression(both_groups, prob_pp_t2_z ~ prob_pp_t1_z + group*phq_8_sum + test_result_fct),
  regression(both_groups, prob_bl_t2_z ~ prob_bl_t1_z + group*phq_8_sum + test_result_fct)
) %>%
  filter(grepl(":", iv)) %>%
  mutate(p_adj = p.adjust(p, "BH")) %>%
  print_nicely(3)
```

### Planned Secondary Analyses

#### Feedback Impact (Content Analysis)

```{r}
feedback_impact_codes <- both_groups %>%
  select(
    starts_with("feedback_impact"), 
    -c(feedback_impact_t1.5, feedback_impact_notes)
  ) %>%
  colnames()

# Frequencies
both_groups %>%
  pivot_longer(cols = feedback_impact_codes) %>%
  group_by(name) %>%
  summarize(
    sum = sum(value),
    pct = percent(mean(value), .1)
  ) %>%
  print_nicely(2)

# Visualized
both_groups %>%
  pivot_longer(cols = feedback_impact_codes) %>%
  mutate(
    name = case_match(
      name,
      "feedback_impact_expected" ~ "Expected",
      "feedback_impact_skeptical" ~ "Skeptical",
      "feedback_impact_surprised" ~ "Surprised",
      "feedback_impact_indifferent" ~ "Indifferent",
      "feedback_impact_misc_good" ~ "Misc. Good",
      "feedback_impact_validated" ~ "Validated",
      "feedback_impact_motivated" ~ "Motivated",
      "feedback_impact_concerned" ~ "Concerned",
      "feedback_impact_curious" ~ "Curious",
      "feedback_impact_sad" ~ "Sad",
      "feedback_impact_unsure" ~ "Unsure",
      "feedback_impact_relieved" ~ "Relieved",
      "feedback_impact_misc_bad" ~ "Misc. Bad"
    )
  ) %>%
  group_by(name) %>%
  summarize(prop = mean(value)) %>%
  arrange(desc(prop)) %>%
  ggplot(aes(reorder(name, prop), prop)) +
  geom_col() +
  scale_x_discrete(name = "Response to Feedback") +
  scale_y_continuous(name = "Frequency", labels = percent) +
  coord_flip() +
  theme_classic()

# Relationship with test result
feedback_impact_codes %>%
  map(
    .f = function(.x) {
      chisq <- chisq.test(table(both_groups[[.x]], both_groups$test_result_fct))
      out <- tibble(
        code = .x,
        freq_mild = mean(both_groups[[.x]][both_groups$test_result_fct == "Mild Depression"], na.rm = T),
        freq_mod = mean(both_groups[[.x]][both_groups$test_result_fct == "Moderate Depression"], na.rm = T),
        freq_sev = mean(both_groups[[.x]][both_groups$test_result_fct == "Moderately Severe or Severe Depression"], na.rm = T),
        x2 = chisq$statistic,
        df = chisq$parameter,
        p = chisq$p.value
      )
      return(out)
    }
  ) %>%
  bind_rows() %>%
  mutate(p_adj = p.adjust(p, "BH"))

# Relationship with change in primary outcomes
out <- tibble()

for(code in feedback_impact_codes) {
  
  for(outcome in c("pc", "tc", "mc", "pp", "bl")) {
    
    formula = as.formula("prob_" %+% outcome %+% "_t2_z ~ prob_" %+% outcome %+% "_t1_z + " %+% code)
    
    reg_out <- regression(feedback_only, formula)
    
    coef <- reg_out %>%
      filter(iv == code)
    
    out <- rbind(out, coef)
    
  }
  
}

out %>%
  mutate(p_adj = p.adjust(p, "BH")) %>%
  arrange(p_adj)

# Relationship with self-labeling
out <- tibble()

for(code in feedback_impact_codes) {
  
  formula = as.formula("self_label_t2_bin ~ self_label_t1 + " %+% code)
  
  reg_out <- glm(
    data = feedback_only,
    formula = formula,
    family = "binomial"
  )
  
  coef <- reg_out %>%
    tidy(exponentiate = T) %>%
    filter(term == code)
  
  out <- bind_rows(out, coef)
  
}

out %>%
  mutate(p_adj = p.adjust(p.value, "BH")) %>%
  arrange(p_adj)
```

#### Heterogeneity in Primary Outcomes

```{r}
# Average change, either direction
mean(abs(feedback_only$prob_pc_t2_z - feedback_only$prob_pc_t1_z))
mean(abs(feedback_only$prob_tc_t2_z - feedback_only$prob_tc_t1_z))
mean(abs(feedback_only$prob_mc_t2_z - feedback_only$prob_mc_t1_z))
mean(abs(feedback_only$prob_pp_t2_z - feedback_only$prob_pp_t1_z))
mean(abs(feedback_only$prob_bl_t2_z - feedback_only$prob_bl_t1_z))

# No significant differences in absolute value of change
t.test(abs(feedback_only$prob_pc_t2 - feedback_only$prob_pc_t1) ~ feedback_only$self_label_t2_bin)
t.test(abs(feedback_only$prob_tc_t2 - feedback_only$prob_tc_t1) ~ feedback_only$self_label_t2_bin)
t.test(abs(feedback_only$prob_mc_t2 - feedback_only$prob_mc_t1) ~ feedback_only$self_label_t2_bin)
t.test(abs(feedback_only$prob_pp_t2 - feedback_only$prob_pp_t1) ~ feedback_only$self_label_t2_bin)
t.test(abs(feedback_only$prob_bl_t2 - feedback_only$prob_bl_t1) ~ feedback_only$self_label_t2_bin)

# Visualized:
feedback_only %>%
  mutate(
    change_pc = (prob_pc_t2 - prob_pc_t1) / sd(prob_pc_t1),
    change_tc = (prob_tc_t2 - prob_tc_t1) / sd(prob_tc_t1),
    change_mc = (prob_mc_t2 - prob_mc_t1) / sd(prob_mc_t1),
    change_pp = (prob_pp_t2 - prob_pp_t1) / sd(prob_pp_t1),
    change_bl = (prob_bl_t2 - prob_bl_t1) / sd(prob_bl_t1)
  ) %>%
  pivot_longer(cols = starts_with("change_")) %>%
  mutate(
    name = factor(
      name,
      levels = c("change_pc", "change_tc", "change_mc", "change_pp", "change_bl"),
      labels = c("Personal Control", "Treatment Control", "Medication Control", "Prognostic Pessimism", "Self-Blame")
    )
  ) %>%
  select(self_label_t2, name, value) %>%
  ggplot() +
  geom_density(
    aes(
      x = value, 
      group = self_label_t2, 
      fill = self_label_t2
    ),
    bw = .25,
    alpha = .25
  ) +
  scale_x_continuous(name = "Change (SD Units)") +
  scale_y_continuous(name = "Density") +
  scale_fill_discrete(name = "Self-Labeling (t2)") +
  facet_wrap(~ name) +
  theme_classic()
```

#### Predicting Help-Seeking

```{r}
feedback_only %>%
  group_by(self_label_t2) %>%
  summarize(opt_in_t2 = percent(mean(opt_in_t2 == "Yes"), .1))

# By self-labeling
oddsratio::or_glm(
  feedback_only,
  glm(
    data = feedback_only,
    formula = (opt_in_t2 == "Yes") ~ self_label_t2,
    family = "binomial"
  )
)

# By test results (and self-labeling)
oddsratio::or_glm(
  feedback_only,
  glm(
    data = feedback_only,
    formula = (opt_in_t2 == "Yes") ~ test_result + self_label_t2,
    family = "binomial"
  )
)

# By group
oddsratio::or_glm(
  both_groups,
  glm(
    data = both_groups,
    formula = (opt_in_t2 == "Yes") ~ group,
    family = "binomial"
  )
)
```

#### Change in Self-Labeling

```{r}
feedback_only %>%
  count(self_label_t2) %>%
  mutate(pct = percent(n / sum(n), .1))

# By baseline
feedback_only %>%
  group_by(self_label_t1) %>%
  count(self_label_t2) %>%
  mutate(pct = percent(n / sum(n), .1))

oddsratio::or_glm(
  feedback_only,
  glm(
    data = both_groups,
    formula = self_label_t2_bin ~ self_label_t1,
    family = "binomial",
  )
)

# By test results
feedback_only %>%
  group_by(test_result_fct) %>%
  count(self_label_t2) %>%
  mutate(pct = percent(n / sum(n), .1))

oddsratio::or_glm(
  feedback_only,
  glm(
    data = both_groups,
    formula = self_label_t2_bin ~ test_result_fct,
    family = "binomial",
  )
)

# By group
oddsratio::or_glm(
  both_groups,
  glm(
    data = both_groups,
    formula = self_label_t2_bin ~ group_char,
    family = "binomial",
  )
)

# Alluvial diagram
library(ggalluvial)
feedback_only %>%
  count(self_label_t1, self_label_t2) %>%
  group_by(self_label_t1) %>%
  mutate(
    combination = paste0(self_label_t1, " -> ", self_label_t2),
    label_left = "n = " %+% n,
    label_right = percent(n / sum(n), .1)
  ) %>%
  pivot_longer(cols = c(self_label_t1, self_label_t2)) %>%
  ggplot(
    aes(
      x = name,
      y = n,
      alluvium = combination, 
      stratum = value
    )
  ) +
  geom_alluvium(aes(fill = value), show.legend = F) +
  geom_stratum() +
  geom_text(stat = "stratum", aes(label = after_stat(stratum))) +
  geom_text(
    stat = "flow", 
    aes(label = ifelse(name == "self_label_t1", label_left, "")),
    position = position_nudge(x = .25)
  ) +
  geom_text(
    stat = "flow", 
    aes(label = ifelse(name == "self_label_t2", label_right, "")),
    position = position_nudge(x = -.25)
  ) +
  scale_x_discrete(name = "Timepoint", labels = c("Before Feedback", "After Feedback")) +
  theme_minimal() +
  theme(
    axis.title.y = element_blank(),
    axis.text.y = element_blank(),
    axis.ticks.y = element_blank(),
    panel.grid.major = element_blank(),
    panel.grid.minor = element_blank()
  )
```

#### Blame and Control

```{r}
# Both groups: baseline
cor.test(both_groups$prob_pc_t1, both_groups$prob_bl_t1)

# Feedback only: baseline and follow-up
cor.test(feedback_only$prob_pc_t1, feedback_only$prob_bl_t1)
cor.test(feedback_only$prob_pc_t2, feedback_only$prob_bl_t2)

# Intervention: baseline and follow-up
cor.test(intervention_only$prob_pc_t1, intervention_only$prob_bl_t1)
cor.test(intervention_only$prob_pc_t2, intervention_only$prob_bl_t2)

library(ggpubr)
both_groups %>%
  ggplot(aes(prob_pc_t2, prob_bl_t2)) +
  geom_jitter(aes(color = group_char), alpha = .5) +
  geom_smooth(aes(color = group_char), formula = y ~ x, method = lm, se = F) +
  stat_cor(method = "pearson") +
  scale_x_continuous(name = "Perceived Personal Control (t2)") +
  scale_y_continuous(name = "Self-Blame (t2)") +
  scale_color_discrete(name = "Group") +
  facet_wrap(~ group_char) +
  theme_classic()
```

#### Qualitative responses

```{r} 
# No self-labeling; why?
both_groups %>%
  distinct(group, test_result, self_label_t2, why_not_no_t2) %>%
  arrange(group, test_result, self_label_t2, why_not_no_t2) %>%
  drop_na() %>%
  kable() %>%
  kable_styling()

# Unsure about self-labeling; why?
both_groups %>%
  distinct(group, test_result, self_label_t2, why_not_unsure_t2) %>%
  arrange(group, test_result, self_label_t2, why_not_unsure_t2) %>%
  drop_na() %>%
  kable() %>%
  kable_styling()

# Advice to other users (and permission to share)
both_groups %>%
  distinct(group, test_result, review_permission, review_advice) %>%
  arrange(group, test_result, review_permission, review_advice) %>%
  drop_na() %>%
  kable() %>%
  kable_styling()

# Talk back to a friend
both_groups %>%
  distinct(group, test_result, review_talk_back) %>%
  arrange(group, test_result, review_talk_back) %>%
  drop_na() %>%
  kable() %>%
  kable_styling()

# Plan (behavior)
both_groups %>%
  distinct(group, test_result, plan_behavior) %>%
  arrange(group, test_result, plan_behavior) %>%
  drop_na() %>%
  kable() %>%
  kable_styling()

# Plan (thoughts)
both_groups %>%
  distinct(group, test_result, plan_thoughts) %>%
  arrange(group, test_result, plan_thoughts) %>%
  drop_na() %>%
  kable() %>%
  kable_styling()
```